---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
library(tidyverse)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# oceandf

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![R build status](https://github.com/paleolimbot/oceandf/workflows/R-CMD-check/badge.svg)](https://github.com/paleolimbot/oceandf/actions)
<!-- badges: end -->

The goal of oceandf is to read ODF files. You can already do this using `oce::read.odf()` and other internal Fisheries and Oceans Canada tools; this package allows more flexible reading using the [readr](https://readr.tidyverse.org) package and using data frames wherever possible.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("paleolimbot/oceandf")
```
## Example

Read ODF files as tables, guessing column types and names from the PARAMTER_HEADER:

```{r example}
library(oceandf)
odf_file <- odf_example("CTD_98911_10P_11_DN.ODF")
read_odf(odf_file)
```

Read ODF headers as a list of tables, guessing column types. This was carefully designed to report parse errors rather than fail for creatively formatted ODF files:

```{r}
read_odf_header(odf_file)
```

The header as a `list()` of `tibble()` makes it particularly well-suited to comparing headers from many files:

```{r}
library(tidyverse)

odf_files <- c(
  odf_example("CTD_98911_10P_11_DN.ODF"),
  odf_example("CTD_PRD2002-001_26_1_DN.ODF")
)

odf_files %>%
  set_names() %>% 
  map_dfr(read_odf_header_tbl, "CRUISE_HEADER", .id = "file")
```
